\documentclass{article}
 
\title{Make Your Own Lithium Power Banks}
\author{Demand for Energy Equality}
%inherited code
\usepackage{amsmath,amsthm,amssymb,epsfig}
\usepackage{hyperref}

% imports for images
\usepackage{caption}
% \usepackage[demo]{graphicx}
\usepackage{graphicx}
% \usepackage{float}

\theoremstyle{definition}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newenvironment{pf}{{\noindent\sc Proof. }}{\qed}

\theoremstyle{definition}
\newtheorem*{defn}{Definition}
\newtheorem*{exmp}{Example}
\newtheorem*{prob}{Problem}
\newtheorem*{info}{Information}
\newtheorem*{warn}{Warning}
\newtheorem*{quest}{Question}
\newtheorem*{blockq}{Block Quote}
\newtheorem*{strong}{Strong}
\newtheorem*{code}{Code}
\newtheorem*{coderesult}{Code Result}

\theoremstyle{remark}
\newtheorem*{rem}{Remark}
\newtheorem*{note}{Note}
\newtheorem*{exer}{Exercise}

\setlength{\oddsidemargin}{0.25 in}
\setlength{\evensidemargin}{-0.25 in}
\setlength{\topmargin}{-0.6 in}
\setlength{\textwidth}{6.5 in}
\setlength{\textheight}{8.5 in}
\setlength{\headsep}{0.75 in}
\setlength{\parindent}{0 in}
\setlength{\parskip}{0.1 in}

%%%%%%%
% Some commonly used notation
%%%%%%%

\def\R{{\mathbb R}}
\def\X{{\mathcal X}}
\def\Y{{\mathcal Y}}
\def\E{{\mathbb E}}
\def\sign{{\rm sign}}

% END inherited code

\begin{document}
 
\maketitle{}

Introductory text

\newpage

\tableofcontents

\newpage

\section{Introduction} % (fold)
\label{sec:introduction}

  \subsection{The Demand Energy Equality project} % (fold)
  \label{sub:the_demand_energy_equality_project}

    Demand Energy Equality (DEE) is a UK based community energy project that seeks to provide practical energy education using solar photovoltaics. We are a group working for systemic change in the way energy is produced, distributed, controlled, delivered and used. These aims are within the context of rising energy inequality (in the UK, at least), rising fuel bills, climate change and the increasing cost of fossil fuel extraction. See \href{https://www.demandenergyequality.org/about/}{our website} to find out more about the project.
    
    Through teaching hands-on energy skills we also aim to develop people’s relationship with energy, and enable them to understand it better; where it comes from, how it is used and how it relates to their needs. Ultimately we aim for this to change behaviour, leading to better use of energy and overall reduced demand. Reduced energy use is an unavoidable fact of the relatively near future – far better to prepare now than be surprised later on.
  
  % subsection the_demand_energy_equality_project (end)
  
  \subsection{Using this guide} % (fold)
  \label{sub:using_this_guide}

    This written guide explains the concepts and techniques involved in making small USB power packs using recovered lithium-ion battery cells. It assumes no prior knowledge of any kind relevant to completing a fully working project. The guide is designed to act as a learning aid for participants on the ‘Make Your Own Lithium Power Bank’ workshops run by Demand Energy Equality, and can be used alongside other DIY guides and resources provided by DEE. 
    
    The guide provides a summary of the basic concepts involved in energy systems, gives an explanation of what lithium cells are and how they can be used, and gives some tips on what you might need to know for larger DIY projects. Links to useful sources of further research are included at the end of the guide.
    
    This particular version reflects the most recent iteration of the process of building a power bank as practiced by DEE, but it is likely that it may evolve and expand over time. Because we occasionally review and update our content, the guide may not always be in line with the other DIY resources published by DEE, and may not exactly reflect the format of current workshops. Contact DEE if you need an update on any recent changes. 
    
    You will find the latest version of this guide available to download from the DEE website, as and when this guide is updated, alongside our \href{https://www.demandenergyequality.org/resources/}{other guides and resources}.
    
    For a chance to gain practical experience of the material covered in this guide, please take a look at the \href{https://www.demandenergyequality.org/our-workshops/}{workshops} offered on the DEE website.
    
    We encourage you to share the skills you learn with others through your own workshops, particularly if you are able to target and work with low-income communities. Please contact us for any support you feel you may need if you plan to do this.
  
  % subsection using_this_guide (end)
  
  \subsection{Disclaimer} % (fold)
  \label{sub:disclaimer}

    This guide is for general guidance only and whilst every effort is made to ensure that the information it contains is correct, it should not be relied upon as accurate. The information / advice contained within this guide is intended for use within the UK only and by persons of no less than 18 years of age. Use this guide at your own risk.
    
    DEE will not accept any liability for any loss, damage, injury or negligence, direct or indirect, from use of the information / advice contained within this guide.
  
  % subsection disclaimer (end)

  \newpage  

% section introduction (end)

\section{Basic concepts} % (fold)
\label{sec:basic_concepts}
  
  \subsection{Power consumption} % (fold)
  \label{sub:power_consumption}
  
  % subsection power_consumption (end)

  \subsection{Voltage} % (fold)
  \label{sub:voltage}
  
  % subsection voltage (end)

  \subsection{Current} % (fold)
  \label{sub:current}
  
  % subsection current (end)

  \subsection{Resistance} % (fold)
  \label{sub:resistance}
  
  % subsection resistance (end)

  \subsection{Series and parallel circuits} % (fold)
  \label{sub:series_and_parallel_circuits}
  
  % subsection series_and_parallel_circuits (end)

  \subsection{Battery capacity} % (fold)
  \label{sub:battery_capacity}
  
  % subsection battery_capacity (end)

% section basic_concepts (end)

\section{Risks and dangers of lithium-ion batteries} % (fold)
\label{sec:risks_and_dangers_of_lithium_ion_batteries}

% section risks_and_dangers_of_lithium_ion_batteries (end)

\section{What are lithium-ion battery cells?} % (fold)
\label{sec:what_are_lithium_ion_battery_cells}

  \subsection{Comparing Lead-acid and Lithium batteries} % (fold)
  \label{sub:comparing_lead_acid_and_lithium_batteries}
  
  % subsection comparing_lead_acid_and_lithium_batteries (end)

  \subsection{Lithium-ion charging} % (fold)
  \label{sub:lithium_ion_charging}
  
  % subsection lithium_ion_charging (end)

  \subsection{Caring for lithium-ion batteries} % (fold)
  \label{sub:caring_for_lithium_ion_batteries}
  
  % subsection caring_for_lithium_ion_batteries (end)

% section what_are_lithium_ion_battery_cells_ (end)

\section{Collecting 18650 cells} % (fold)
\label{sec:collecting_18650_cells}

  \subsection{Where to find second hand 18650 lithium cells} % (fold)
  \label{sub:where_to_find_second_hand_18650_lithium_cells}
  
  % subsection where_to_find_second_hand_18650_lithium_cells (end)

  \subsection{18650 cell configurations} % (fold)
  \label{sub:18650_cell_configurations}
  
  % subsection 18650_cell_configurations (end)

  \subsection{How to safely recover 18650 lithium-ion cells from a laptop battery} % (fold)
  \label{sub:how_to_safely_recover_18650_lithium_ion_cells_from_a_laptop_battery}
  
  % subsection how_to_safely_recover_18650_lithium_ion_cells_from_a_laptop_battery (end)

  \subsection{How to test 18650 cells} % (fold)
  \label{sub:how_to_test_18650_cells}
  
  % subsection how_to_test_18650_cells (end)

% section collecting_18650_cells_ (end)

\section{Building a USB power bank} % (fold)
\label{sec:building_a_usb_power_bank}

% section building_a_usb_power_bank (end)

\section{Building a bigger battery pack} % (fold)
\label{sec:building_a_bigger_battery_pack}

% section building_a_bigger_battery_pack (end)

\section{Lithium battery chemistries, applications and form factors} % (fold)
\label{sec:lithium_battery_chemistries_applications_and_form_factors}

% section lithium_battery_chemistries_applications_and_form_factors (end)

\section{Resources} % (fold)
\label{sec:resources}

  \subsection{Useful Information On Lithium Cells} % (fold)
  \label{sub:useful_information_on_lithium_cells}
  
  % subsection useful_information_on_lithium_cells (end)

  \subsection{Other Renewable Energy Resources} % (fold)
  \label{sub:other_renewable_energy_resources}
  
  % subsection other_renewable_energy_resources (end)

  \subsection{Lithium battery suppliers for off grid systems} % (fold)
  \label{sub:lithium_battery_suppliers_for_off_grid_systems}
  
  % subsection lithium_battery_suppliers_for_off_grid_systems (end)

% section resources (end)

\end{document}